**Introducing the Choice-Confidence (CHOCO) Model for Bimodal Scales Data: Application to the Relationship between Reality Beliefs about AI-Generated Faces and Beauty**

### 2025-05-06 analysis/1_study1.qmd
update what I have
@AnafNeves I'm pushing what I have if you want to take a look at the ms draft

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)
library(cmdstanr)
library(rstan)

set.seed(123)
```

@@

dfraw <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace/refs/heads/main/data/data.csv") |> 
  mutate(Real = (Belief_Answer + 1) / 2,  # Rescale
         Orientation = ifelse(Sexual_Orientation == "Straight ", "Heterosexual", Sexual_Orientation),
         Item = gsub(".jpg", "", Stimulus)) |> 
  filter(Sex %in% c("Male", "Female"), Orientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |> 
  mutate(Relevance = case_when(
    Sex == "Male" & Orientation == "Heterosexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Heterosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Bisexual" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Bisexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Male" & Orientation == "Homosexual" & grepl("NM", Stimulus) ~ "Relevant",
    Sex == "Female" & Orientation == "Homosexual" & grepl("NF", Stimulus) ~ "Relevant",
    .default = "Irrelevant"
  )) |> 
  mutate(SexOrientation = paste(Sex, "-", Orientation)) |>
  filter(Relevance == "Relevant", Orientation == "Heterosexual")

>>>>

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(brms)
library(cmdstanr)
library(rstan)
```

@@

set.seed(123)

dfraw <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace/refs/heads/main/data/data.csv") |> 
  mutate(Real = (Belief_Answer + 1) / 2,  # Rescale
         Orientation = ifelse(Sexual_Orientation == "Straight ", "Heterosexual", Sexual_Orientation),
         Item = gsub(".jpg", "", Stimulus)) |> 
  filter(Sex %in% c("Male", "Female"), Orientation %in% c("Heterosexual", "Bisexual")) |> 
  mutate(Relevance = case_when(
    Sex == "Male" & grepl("NF", Stimulus) ~ "Relevant",
    Sex == "Female" & grepl("NM", Stimulus) ~ "Relevant",
    .default = "Irrelevant"
  )) |> 
  mutate(SexOrientation = paste(Sex, "-", Orientation)) |> 
  filter(Relevance == "Relevant")

### 2025-05-06 analysis/2_study2.qmd
update what I have
@AnafNeves I'm pushing what I have if you want to take a look at the ms draft

  p <- modelbased::estimate_prediction(m, data = newdata, predict = "mu", iterations = 50)
  confright <- modelbased::estimate_prediction(m, data = newdata, predict = "confright", iterations = 50)
  confleft <- modelbased::estimate_prediction(m, data = newdata, predict = "confleft", iterations = 50)
  precright <- modelbased::estimate_prediction(m, data = newdata, predict = "precright", iterations = 50)
  precleft <- modelbased::estimate_prediction(m, data = newdata, predict = "precleft", iterations = 50)
  pex <- modelbased::estimate_prediction(m, data = newdata, predict = "pex", iterations = 50)
  bex <- modelbased::estimate_prediction(m, data = newdata, predict = "bex", iterations = 50)
  if ("pmid" %in% names(insight::find_parameters(m))) {
    pmid <- modelbased::estimate_prediction(m, data = newdata, predict = "pmid", iterations = 50)
  } else {
    pmid <- list(Predicted = rep(0, nrow(newdata)))
  }

@@

df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace2/refs/heads/main/data/data_task.csv") |> 
  filter(Relevance == "Relevant") |> 
  mutate(Real = (Realness + 3) / 6,
         Attractive = Attractiveness / 6,
         Beauty = Beauty / 6,
         RealNoex = datawizard::change_scale(Real, to = c(0.125, 0.875))) |> 
  select(Participant, Sex=Gender, Condition, Item=Stimulus, Real, RealNoex, Attractive, Beauty)

write.csv(df, "../data/sample2.csv", row.names = FALSE)
```

@@

```{r}
m <- lme4::lmer(Real ~ Sex / poly(Attractive, 2) * Condition + (1|Participant) + (1|Item), data = df)
display(parameters::parameters(m, effects = "fixed"))

estimate_relation(m, length = 30) |> 
  ggplot(aes(x=Attractive, y = Predicted)) + 
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high,, fill = Condition), alpha = 0.2) +
  geom_line(aes(color = Condition), linewidth = 1) +
  geom_smooth(data=df, aes(color = Condition, y = Real), method = "loess", se = FALSE, linetype = "dotted", formula = 'y ~ x') +
  scale_color_manual(values = c("AI-Generated"="#3F51B5", "Photograph"="#FF5722")) +
  scale_fill_manual(values = c("AI-Generated"="#3F51B5", "Photograph"="#FF5722")) +
  facet_wrap(~Sex) +
  theme_minimal()
```

#### Posterior Predictive Check

```{r}
m2_chocoat <- readRDS("models/sample2_chocoattractiveness.rds")

m <- m2_chocoat

make_ppcheck  <- function(m, fill = "#FF9800") {
  pred <- m |> 
    modelbased::estimate_prediction(df, keep_iterations = 100, iterations = 100) |>
    select(Sex, starts_with("iter_")) |> 
    bayestestR::reshape_iterations()

  pred |>
    ggplot(aes(x = iter_value)) +
    stat_bin(data = df, aes(x = Real, y = after_stat(density)),
             geom="bar", breaks = seq(0, 1.0, by = 0.04), fill = "#424242") +
    stat_bin(aes(group = iter_group, y = after_stat(density)), position = "identity",
             geom="bar", breaks = seq(0, 1.0, by = 0.04), pad = TRUE,
             alpha = 0.01, fill = fill) +

@@

make_ppcheck(m2_chocoat) +
  labs("Real")
```

@@

```{r}
# c <- estimate_contrasts(m2_chocoat, contrast = "Condition", by = "Sex", predict = "mu")
# c <- estimate_contrasts(m2_chocoat, contrast = "Condition", by = "Sex", predict = "mu", backend = "emmeans")
# c2 <- estimate_contrasts(m2_chocoat, contrast = "Condition", by = "Sex", predict = "confright", backend = "emmeans")
```

@@

```{r}
pred <- visualize_dchoco(m2_chocoat,
                         newdata=insight::get_datagrid(m2_chocoat, length = 5, preserve_range = FALSE),
                         x = seq(0, 1, length.out=7))

p4_density <- pred$densities |> 
  mutate(Attractive = as.factor(Attractive),
         y = ifelse(x %in% c(0, 1), y * 3, y),  # Inflate extremes for visibility
         x = ifelse(Condition == "AI-Generated", x + 0.1, x)) |>  
  filter(Condition == "Photograph") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color=Attractive), linewidth = 1.25) +
  geom_path(data = filter(pred$mu, Condition == "Photograph"), aes(group = side), linewidth=0, lineend = 'round', 
            arrow = arrow(length = unit(0.025, "npc"), type = "closed")) +
  facet_wrap(~Sex) +
  labs(y = "Distribution", x = "Do you think this image is real?", color = "Attractiveness") +
  scale_colour_manual(values=scales::seq_gradient_pal("#FFCDD2", "#B71C1C", "Lab")(seq(0,1,length.out=5))) +
  scale_x_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("      0%", "25%", "50%", "75%", "100%      ")) +
  scale_linewidth_continuous(range = c(0.5, 2), guide = "none") +
  theme_minimal() +
  theme(axis.title.x = element_text(face = "bold"), 
        axis.text.y = element_blank(), 
        # axis.title.y = element_blank(), 
        strip.background = element_rect(fill = "lightgrey", color = NA)) 
p4_density
```

@@

## Figures

>>>>

  p <- modelbased::estimate_prediction(m, data = newdata, predict = "mu", iterations = 50)
  confright <- modelbased::estimate_prediction(m, data = newdata, predict = "confright", iterations = 50)
  confleft <- modelbased::estimate_prediction(m, data = newdata, predict = "confleft", iterations = 50)
  precright <- modelbased::estimate_prediction(m, data = newdata, predict = "precright", iterations = 50)
  precleft <- modelbased::estimate_prediction(m, data = newdata, predict = "precleft", iterations = 50)
  if ("pex" %in% names(insight::find_parameters(m))) {
    pex <- modelbased::estimate_prediction(m, data = newdata, predict = "pex", iterations = 50)
  } else {
    pex <- list(Predicted = rep(0, nrow(newdata)))
  }
  if ("bex" %in% names(insight::find_parameters(m))) {
    bex <- modelbased::estimate_prediction(m, data = newdata, predict = "bex", iterations = 50)
  } else {
    bex <- list(Predicted = rep(0.5, nrow(newdata)))
  }
  if ("pmid" %in% names(insight::find_parameters(m))) {
    pmid <- modelbased::estimate_prediction(m, data = newdata, predict = "pmid", iterations = 50)
  } else {
    pmid <- list(Predicted = rep(0, nrow(newdata)))
  }

@@

set.seed(123)

dfraw <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace2/refs/heads/main/data/data_task.csv") |> 
  full_join(read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace2/refs/heads/main/data/data_participants.csv") |> 
              select(Participant, Age), by = "Participant") |> 
  rename(Sex = Gender, Orientation = SexualOrientation, Item=Stimulus) |> 
  filter(Sex %in% c("Male", "Female"), Orientation %in% c("Heterosexual", "Bisexual")) |> 
  mutate(Relevance = case_when(
    Sex == "Male" & grepl("NF", Item) ~ "Relevant",
    Sex == "Female" & grepl("NM", Item) ~ "Relevant",
    .default = "Irrelevant"
  ))  |> 
  filter(Relevance == "Relevant") |> 
  mutate(Real = (Realness + 3) / 6,
         Attractive = Attractiveness / 6,
         Beauty = Beauty / 6,
         RealNoex = datawizard::change_scale(Real, to = c(0.125, 0.875)),
         SexOrientation = paste(Sex, "-", Orientation))

dfraw |> 
  select(Participant, Sex, Condition, Item, Real, RealNoex, Attractive, Beauty) |> 
  write.csv("../data/sample2.csv", row.names = FALSE)
```

# For demographic section
dfraw |> 
  mutate(n_stims = n(), .by = "Participant") |> 
  select(Participant, Age, Sex, n_stims) |> 
  slice(1, .by = "Participant") |> 
  report::report_participants()

report::report(dfraw$Sex)
```

@@

```{r}
ggplot(df, aes(x=Real)) +
  geom_bar() +
  facet_wrap(~Sex)
```

```{r}
m <- lme4::lmer(RealNoex ~ Sex / poly(Attractive, 2) * Condition + (1|Participant) + (1|Item), data = df)
display(parameters::parameters(m, effects = "fixed"))

estimate_relation(m, length = 30) |> 
  ggplot(aes(x=Attractive, y = Predicted)) + 
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high,, fill = Condition), alpha = 0.2) +
  geom_line(aes(color = Condition), linewidth = 1) +
  geom_smooth(data=dfraw, aes(color = Condition, y = Real), method = "loess", se = FALSE, linetype = "dotted", formula = 'y ~ x') +
  scale_color_manual(values = c("AI-Generated"="#3F51B5", "Photograph"="#FF5722")) +
  scale_fill_manual(values = c("AI-Generated"="#3F51B5", "Photograph"="#FF5722")) +
  facet_wrap(~Sex) +
  theme_minimal()
```

#### Model Comparison

```{r}
# m2_betagate <- readRDS("models/sample2_betagate.rds")
m2_betagate <- readRDS("models/sample2noex_betagate.rds")
m2_chocoat <- readRDS("models/sample2_chocoattractiveness.rds")
m2_chocoat <- readRDS("models/sample2noex_chocoattractiveness.rds")
```

```{r}
loocomp <- loo::loo_compare(m2_betagate, m2_chocoat, criterion = "waic")

parameters(loocomp, include_ENP = TRUE)

report::report(loocomp)
```

##### Posterior Predictive Check

```{r}
make_ppcheck  <- function(m, fill = "#FF9800") {
  pred <- m |> 
    modelbased::estimate_prediction(df, keep_iterations = 100, iterations = 100) |>
    select(Sex, starts_with("iter_")) |> 
    bayestestR::reshape_iterations()

  pred |>
    ggplot(aes(x = iter_value)) +
    stat_bin(data = df, aes(x = RealNoex, y = after_stat(density)),
             geom="bar", breaks = seq(0, 1.0, by = 0.04), fill = "#424242") +
    stat_bin(aes(group = iter_group, y = after_stat(density)), position = "identity",
             geom="bar", breaks = seq(0, 1.0, by = 0.04), pad = TRUE,
             alpha = 0.01, fill = fill) +

@@

p_ppc1 <- make_ppcheck(m2_chocoat, fill = "brown") +
  labs("Real") 
p_ppc2 <- make_ppcheck(m2_betagate, fill = "#FF9800") +
  labs("Real")

p_ppc1 / p_ppc2 
```

@@

```{r}
c <- data.frame()
for(param in c("mu", "confright", "confleft", "precright", "precleft", "pmid")) {
  c <- estimate_contrasts(m2_chocoat, contrast = "Condition", by = "Sex", predict = param, backend = "emmeans") |>
    mutate(Parameter = ifelse(param == "mu", "p", param)) |> 
    rbind(c)
}
c
```

@@

```{r}
pred <- visualize_dchoco(m2_chocoat,
                         newdata=insight::get_datagrid(m2_chocoat, length = 5, preserve_range = FALSE),
                         x = seq(0, 1, length.out=9))

p4_density <- pred$densities |> 
  mutate(Attractive = as.factor(Attractive),
         y = ifelse(x %in% c(0, 1), y * 3, y),  # Inflate extremes for visibility
         x = ifelse(Condition == "AI-Generated", x + 0.01, x)) |>  
  filter(Condition == "Photograph") |>
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color=Attractive, linetype = Condition), linewidth = 1.25) +
  # geom_path(data = filter(pred$mu, Condition == "Photograph"), aes(group = side), linewidth=0, lineend = 'round', 
  #           arrow = arrow(length = unit(0.025, "npc"), type = "closed")) +
  facet_wrap(~Sex) +
  labs(y = "Distribution", x = "Do you think this image is real?", color = "Attractiveness") +
  scale_colour_manual(values=scales::seq_gradient_pal("#FFCDD2", "#B71C1C", "Lab")(seq(0,1,length.out=5))) +
  scale_x_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("      0%", "25%", "50%", "75%", "100%      ")) +
  scale_linewidth_continuous(range = c(0.5, 2), guide = "none") +
  theme_minimal() +
  theme(axis.title.x = element_text(face = "bold"), 
        axis.text.y = element_blank(), 
        # axis.title.y = element_blank(), 
        strip.background = element_rect(fill = "lightgrey", color = NA)) 
p4_density
```

@@

```{r}
m2_chocobeauty <- readRDS("models/sample2noex_chocobeauty.rds")
params_table(m2_chocobeauty, keep = "polyBeauty|Condition")
```

:::
## Figures

### 2025-05-06 paper/manuscript.qmd
update what I have
@AnafNeves I'm pushing what I have if you want to take a look at the ms draft

The sample is the same as in [@makowski2025too]. We included all heterosexual male and female participants, for a final sample of 125 participants (Mean age = 28.6, SD = 9.2, range: [19, 66]; Sex: 44.8% females). We included only sexually relevant stimuli for men and women (i.e., all 89 female faces for men and 20 male faces for women).

@@

The models did converge without divergent transitions, and the effective sample size was sufficient for all parameters (all $n_{\text{eff}} > 1000$).
The difference in predictive accuracy, as indexed by Expected Log Predictive Density (ELPD-WAIC), suggests that the *CHOCO* is the best
model ($ELPD = -138.45$), followed by *Beta-Gate* ($\Delta_{ELPD} = -1875.31 \pm 61.18, p < .001)$ and *ZOIB* ($\Delta_{ELPD} = -1916.11 \pm 61.75, p < .001$). See @fig-three for the posterior predictive checks, showing that only the CHOCO model managed to capture the bimodal distribution of data.

@@

The ZOIB model suggested that women had higher mean (*mu* parameter) scores of reality beliefs ($\Delta_{\text{Female}} = 0.16,~95\%~ CI~[0.01, 0.32], pd = 98.10\%$), less extreme values (*zoi* parameter; STATS) but more ones relative to zeros (*coi* parameter; STATS).

@@

The ZOIB model estimated reliable variability in the participant's *phi* parameter (D-vour = 0.88) and *zoi* parameter (D-vour = 0.84), as well as in the *mu* parameter related to individual items (D-vour = 0.82). Moderate reliability was also observed for items in the *coi* parameter (D-vour = 0.71) and for participants in the *mu* parameter (D-vour = 0.69). The Beta-Gate model yielded similar results: a high reliability of participant's *phi* parameter (D-vour = 0.88), *pex* parameter (D-vour = 0.84). The *mu* parameter's variability was reliably captured for items (D-vour = 0.85) and moderately for participants (D-vour = 0.72). 
Of note that the parameters of Beta-Gate and ZOIB correlate almost perfectly, underlining their empirical similarity despite a different parametrization.

The CHOCO model yielded reliable estimates for all parameters except *bex* for participants (*confright* D-vour = 0.94, *confleft* D-vour = 0.91, *pex* D-vour = 0.80, *p* D-vour = 0.73, *precright* D-vour = 0.79, *precleft* D-vour = 0.73). Item's variability was primarily reflected through the *p* parameter (D-vour = 0.86).

Finally, the empirical average correlated the most strongly with CHOCO's *p* (r = .94), rather than ZOIB's *mu* (r = .74) or
Beta-Gate's *mu* (r = .82). The empirical overall confidence was the strongest correlated with CHOCO's *confright* (r = .91), followed by ZOIB's *phi* (r = -.86), Beta-Gate's phi (r = -.83), and other CHOCO's parameters. The empirical proportion of "right" answer *p* correlated the strongest with CHOCO's *p* (r = 0.94), followed by Beta-Gate's *mu* (r = .82) and ZOIB's *mu* (r = .77). The empirical *pex* correlated the strongest with ZOIB's *zoi* (r = .90), and Beta-Gate's *pex* (r = .90), and CHOCO's *pex* (r = .88).

@@

The first sample includes the same participants as study 1 (see above). 
**TODO** for sample 2.

@@

In sample 1, the traditional approach suggested a significant linear relationship between the mean level of "Reality" and attractiveness ($\beta_{poly1}=3.63, ~95\%~CI [2.71, 4.56], pd = ...\%$) for males only. The CHOCO model revealed that attractiveness had a significantly positive linear relationship with the probability *p* of judging faces as real (STATS), but a quadratic relationship with the confidence in real judgments (*confright*; STATS). Attractiveness was also associated with less confidence in fake judgments (*confleft*; STATS), and related linearly with a stronger bias towards extreme Real responses (*bex*; STATS). These effects were present for males only, and no relationship was found for females. The reliability of the effect of attractiveness (the random slopes) was very low for all parameters (D-vour < 0.1).

The effect of Beauty was the same as above, with some additional evidence in favour of an effect in women, in particular for a linear relationship with *p* for females as well ($\beta_{poly1}=7.02, ~95\%~CI [-0.90, 14.97], pd = 95.91\%$), as well as a quadradic relationship with the confidence in fake judgments (*confleft*; STATS).

@@

@@

@@

>>>>

The sample is the same as in [@makowski2025too]. We included all heterosexual and bisexual (these two groups did not seem to differ based on preliminary analyses and were thus grouped to maximize power) male and female participants, for a final sample of 141 participants (Mean age = 28.4, SD = 9.0, range: [19, 66]; Sex: 47.5% females). For each participant, we included only stimuli of the opposite gender (i.e., all 89 female faces for men and 20 male faces for women).

@@

The models did converge without divergent transitions, and the effective sample size was sufficient for all parameters (all $n_{\text{eff}} > 1000$).
The difference in predictive accuracy, as indexed by Expected Log Predictive Density (ELPD-WAIC), suggests that the *CHOCO* is the best
model ($ELPD = -203.54$), followed by *Beta-Gate* ($\Delta_{ELPD} = -1794.57 \pm 63.12, p < .001)$ and *ZOIB* ($\Delta_{ELPD} = -1833.59 \pm 63.52, p < .001$). See @fig-three for the posterior predictive checks, showing that only the CHOCO model managed to capture the bimodal distribution of data.

@@

The ZOIB model suggested that women had higher mean (*mu* parameter) scores of reality beliefs ($\Delta_{\text{Female}} = 0.20,~95\%~ CI~[0.03, 0.37], pd = 98.77\%$), less extreme values (*zoi* parameter; STATS) but more ones relative to zeros (*coi* parameter; STATS).

@@

The ZOIB model estimated reliable variability in the participant's *phi* parameter (D-vour = 0.88) and *zoi* parameter (D-vour = 0.85), as well as in the *mu* parameter related to individual items (D-vour = 0.82). Moderate reliability was also observed for items in the *coi* parameter (D-vour = 0.71) and for participants in the *mu* parameter (D-vour = 0.69). The Beta-Gate model yielded similar results: a high reliability of participant's *phi* parameter (D-vour = 0.88), *pex* parameter (D-vour = 0.85). The *mu* parameter's variability was reliably captured for items (D-vour = 0.85) and moderately for participants (D-vour = 0.72).

The CHOCO model yielded reliable estimates for all parameters except *bex* for participants (*confright* D-vour = 0.94, *confleft* D-vour = 0.91, *pex* D-vour = 0.79, *p* D-vour = 0.73, *precright* D-vour = 0.77, *precleft* D-vour = 0.67). Item's variability was primarily reflected through the *p* parameter (D-vour = 0.86).

Finally, the empirical average correlated the most strongly with CHOCO's *p* (r = .86), rather than ZOIB's *mu* (r = .77) or
Beta-Gate's *mu* (r = .82). The empirical overall confidence was the strongest correlated with CHOCO's *confright* (r = .91), followed by ZOIB's *phi* (r = -.86), Beta-Gate's phi (r = -.83), and other CHOCO's parameters. The empirical proportion of "right" answer *p* correlated the strongest with CHOCO's *p* (r = 0.94), followed by Beta-Gate's *mu* (r = .82) and ZOIB's *mu* (r = .77). The empirical *pex* correlated the strongest with ZOIB's *zoi* (r = .90), and Beta-Gate's *pex* (r = .90), and CHOCO's *pex* (r = .88).
Of note that the parameters of Beta-Gate and ZOIB correlate almost perfectly, underlining their empirical similarity despite a different parametrization.

@@

The first sample includes the same participants as study 1 (see above).

**TODO** for sample 2.

The final sample included 189 participants (Mean age = 28.4, SD = 14.0, range: [18, 69]; Sex: 76.2% females).

@@

### Sample 1

In sample 1, the traditional approach suggested a significant linear relationship between the mean level of "Reality" and attractiveness ($\beta_{poly1}=3.42, ~95\%~CI [2.50, 4.34], p < .001\%$) for males only. The CHOCO model revealed that attractiveness had a significantly positive linear relationship with the probability *p* of judging faces as real (STATS), but a quadratic relationship with the confidence in real judgments (*confright*; STATS). Attractiveness was also associated with less confidence in fake judgments (*confleft*; STATS), a quadratic relationship with left precision (*precleft*; STATS), and related linearly with a stronger bias towards extreme Real responses (*bex*; STATS). These effects were present for males only, and no relationship was found for females. The reliability of the effect of attractiveness (the random slopes) was very low for all parameters (D-vour < 0.01). 
The effect of Beauty was the same as of attractiveness.

<!-- , with some additional evidence in favour of an effect in women, in particular for a linear relationship with *p* for females as well ($\beta_{poly1}=7.02, ~95\%~CI [-0.90, 14.97], pd = 95.91\%$), as well as a quadratic relationship with the confidence in fake judgments (*confleft*; STATS). -->

### Sample 2

@@

This study introduces a new statistical model to analyze bimodal data, which can be observed for instance when using subjective rating scales in which the two sides correspond to a different "choice" (e.g., "false" vs. "true", "real" vs "fake").  The Choice-Confidence (CHOCO) model conceptualizes the data as a mixture of two distributions, one for each choice, and models the probability of choosing one or the other as well as the degree of confidence in each choice. We validated this model on real-life data by appling it to the reality beliefs of @makowski2025too, and showed that it was able to capture the bimodal nature of the data and provides a more accurate representation of the underlying processes than other alternative approaches, including Zero-or-One inflated Beta (ZOIB) models.

@@

We demonstrated the flexibility of the CHOCO model, being usable in analog scales as well as discrete ratings with a mid-point.

@@

Future studies should assess psychometric property liek the minimum amount of data required to estimate all parameters reliably.
